---
title: "Usage of fars package"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# Package Description

`fars` package reads and plots Fatality Analysis Reporting System (FARS) data 
from the [National Highway Traffic Safety 
Administration](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars).

[FARS](https://en.wikipedia.org/wiki/Fatality_Analysis_Reporting_System) is a
nationwide census, providing the American public yearly data, regarding fatal
injuries suffered in motor vehicle traffic crashes.


## Load Packages

```{r}
library(fars)
library(maps)
library(dplyr)
```


## Included data

Data files included within the package are:

```{r}
list.files(system.file("inst","extdata", package = "fars"))
```


## Package Functions

### Function `make_filename`

This function returns file name and path to the data files:

```{r}
yr <- 2015
make_filename(yr)
```

### Function `fars_read_years`

This functiuon will read in multiple Fatality Analysis Reporting System data files based on the years provided.

```{r}
fars_read_years(2013)
```


### Function `fars_summarize_years`

This function summarizes yearly accidents data, by month.

```{r}
plot(fars_summarize_years(2015))
fars_summarize_years(c(2015, 2014))
```

### Function `fars_map_state`

The function displays a state map plot including accidents location
by year

```{r}
state_num <- 49 # Utah
yr <- 2014
fars_map_state(state_num, yr)
```
